Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/metalang.tex
Update metalang.tex

  encodeygc(sa, sb) {
    let owl1 = owl(sa) in
    let owl2 = owl(sb) in
    v[1,gate: || sa || 1.k] := OT(s[1,sa],owl1.k,(not owl1.k));
    v[1,gate: || sa || 1.p] := OT(s[1,sa],owl1.p,(not owl1.p));
    v[1,gate: || sb || 2.k] := select(s[2,sb],owl2.k,(not owl2.k));
    v[1,gate: || sb || 2.p] := select(s[2,sb],owl2.p,(not owl2.p));
    { wv1 = { k = v[1,"gate:" || sa || "1.k"]; p = v[1,"gate:" || sa || "1.p"] };
      wv2 = { k = v[1,"gate:" || sb || "2.k"]; p = v[1,"gate:" || sb || "2.p"] } }
  }

@@

    \ttt{\{ k = not flip[2,"gate:6.k"]; p =  not flip[2,"gate:6.p"]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository \cite{jpdf-github}.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}

>>>>

  encodeygc(sa, sb) {
    let owl1 = owl(sa) in
    let owl2 = owl(sb) in
    v[1,"gate:" || sa || "1.k"] := OT(s[1,sa],owl1.k,(not owl1.k));
    v[1,"gate:" || sa || "1.p"] := OT(s[1,sa],owl1.p,(not owl1.p));
    v[1,"gate:" || sb || "2.k"] := select(s[2,sb],owl2.k,(not owl2.k));
    v[1,"gate:" || sb || "2.p"] := select(s[2,sb],owl2.p,(not owl2.p));
    { wv1 = { k = v[1,"gate:" || sa || "1.k"]; p = v[1,"gate:" || sa || "1.p"] };
      wv2 = { k = v[1,"gate:" || sb || "2.k"]; p = v[1,"gate:" || sb || "2.p"] } }
  }

@@

    \ttt{\{ k = not flip[2,"gate:6.k"]; p =  not flip[2,"gate:6.p"]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,"gate:6tt2"]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository \cite{jpdf-github}.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}
